---
title: "Burden of Care Analysis Report"
author: "Maria Anderson and David Brocker"
format: 
  html:
    code-fold: true
    code-link: true
    code-tools: true
    toc: true
    toc-depth: 3
editor: visual
theme:
  light: flatly
  dark: darkly
---

```{r}
#| echo: false
#| warning: false
#| message: false
library(afex)
library(dplyr)
library(janitor)
library(broom)
library(huxtable)
library(ggplot2)
library(ggbeeswarm)
library(wesanderson)
```

```{r}
# Hux Wrapper: Correlation
hux_corr <- function(ct){
  if(!class(ct) == "htest"){
    print("Source must be of class 'htest'")
  } else{
    ct |> 
      broom::tidy() |> 
      mutate(
        `CI[LL,UU]` = paste0("[",conf.low |> round(2),
                             ",",conf.high |> round(2),
                             "]")
      ) |> 
      rename(
        r = estimate,
        t = statistic, 
        p = p.value, 
        df = parameter,
      ) |> 
      relocate(
        p, .after = df
      ) |>
      relocate(
        alternative, .after = last_col()
      ) |> 
      select(-conf.low,-conf.high,-method) |> 
      hux() |> 
      theme_article()
  }
}

# t-test Wrapper
hux_tt <- function(ttest,grp1,grp2){
  if (!class(ttest)=="htest"){
    print("Object is not a t-test")
  } else {
    ttest |> 
      broom::tidy() |> 
      rename(
        M_Diff = estimate,
        t = statistic,
        p = p.value,
        df = parameter,
        grp1 = estimate1,
        grp2 = estimate2
        ) |> 
      mutate(
        `CI[ll,uu]` = paste0("[",round(conf.low,2),",",round(conf.high,2),"]")
      ) |>
      select(!conf.low:alternative) |> 
      relocate(p, .after = `CI[ll,uu]`) |> 
      hux() |> 
      theme_article()
  }
}

# Continous Scales
cont_skim <- function(data){
  sk <- 
    data |> 
    # Data is Rowwise from cleaning
    ungroup() |> 
    skim() |> 
    # Remove skim_type
    yank("numeric") |> 
    # Make everything Look Like This
    rename_with(str_to_sentence) |> 
    rename(
      M = Mean,
      SD = Sd,
      Missing = N_missing,
      Variable = Skim_variable
    ) |>
    # Remove Quartile Columns
    dplyr::select(!(starts_with("P"))) |> 
    hux() |> 
    theme_article() |> 
    set_align(everywhere,everywhere,"center") |> 
    set_align(row = everywhere, col = 1, value = "left")
  
  return(sk)
}

# Discrete Scales
discrete_tab <- function(data,x,lab){
  name <- 
    data |> 
    dplyr::select({{x}}) |> 
    pull() 
  
  tab <- 
    name |> 
    tabyl() |> 
    dplyr::select(-(starts_with("val"))) |> 
    # Ignore Error for Now,,,
    adorn_pct_formatting(,,,percent) |> 
    rename_with(str_to_sentence) |> 
    hux() |> 
    theme_article() |> 
    set_align(everywhere,everywhere,".")

  # Change header row to Variable | | 
  tab[1,] <- c(str_to_sentence(x),"","")
  
  # Get Number of Rows
  to_in <- nrow(tab)
  
  tab[2:to_in,1] <- lab

  return(tab)
}

# Set Theme Structure
theme_set(theme_minimal())

theme_update(
  plot.background = element_rect(fill = "#fafaf5", color = "#fafaf5"),
  panel.background = element_rect(fill = NA, color = NA),
  panel.border = element_rect(fill = NA, color = NA),
)
```

# Study Design

-   IV's

    -   Negative Prime Scramble

    -   Positive Prime Scramble

-   DV's

    -   Burden Scale for Family Caregivers

    -   Positive Aspects of Caregiving

    -   Dementia Attitude's Scale

    -   Healthy Days Score

    -   Years as a Caregiver

    -   Confidence in Ability to Provide Care

    -   Support Received from Friends/Family

# Hypotheses

## Negative/Positive Prime

-   H1:

    -   Plan:

-   H2:

    -   Plan:

-   H3:

    -   Plan:

-   H4:

    -   Plan:

-   H5:

    -   Plan:

-   H6:

    -   Plan:

### Data Cleaning

```{r}
# Read in file
cg <- read.csv("Data Analysis Caregiver Study.xlsx - Correlations.csv")

# Clean Data
cg_cln <- 
  cg |>
  # Rename variables
  rename(
    condition = Condition...Positive...1..Negative...2,
    years_as_cg = X..years.as.caregiver,
    support = Support..Do.you.feel.like.you.have.adequate.support.from.others.in.your.life..0...no..1...somewhat..2...yes,
    confidence = confidence.1.not.confident.5.very.confident,
    hd_gen = hd_genWould.you.say.that.in.general.your.health.is...,
    hd_phys = hd_physHow.many.days.during.the.past.30.days.was.your.physical.health.not.good.,
    hd_men = hd_menHow.many.days.during.the.past.30.days.was.your.mental.health.not.good.,
    hd_usual = hd_usualDuring.the.past.30.days..for.about.how.many.days.did.poor.physical.or.mental.health.keep.you.from.doing.your.usual.activities..such.as.self.care..work..or.recreation.,
    hd_pain = hd_painDuring.the.past.30.days..for.about.how.many.days.did.PAIN.make.it.hard.for.you.to.do.your.usual.activities..such.as.selfcare..work..or.recreation.,
    hd_sad = hd_sadDuring.the.past.30.days..for.about.how.many.days.have.you.felt.SAD..BLUE..or.DEPRESSED.,
    hd_worried = hd_worriedDuring.the.past.30.days..for.about.how.many.days.have.you.felt.WORRIED..TENSE..or.ANXIOUS.,
    hd_sleep = hd_sleepDuring.the.past.30.days..for.about.how.many.days.have.you.felt.you.did.NOT.get.ENOUGH.REST.or.SLEEP.,
    hd_energy = hd_energyDuring.the.past.30.days..for.about.how.many.days.have.you.felt.VERY.HEALTHY.AND.FULL.OF.ENERGY.
  ) |> 
  # Clean Names
  clean_names()
```

### Correlations

#### Years as Caregiver x Positive Aspects of Caregiving

```{r}
cor.test(cg_cln$years_as_cg,cg_cln$paoc) |> 
  hux_corr()
```

#### Years as Caregiver x Burden Scale for Family Caregivers

```{r}
# Years x BSFC
cor.test(cg_cln$years_as_cg, cg_cln$bsfc) |> 
hux_corr()
```

#### Level of Confidence x Positive Aspects of Caregiving

```{r}
# Confidence x PAOC
cor.test(cg_cln$confidence, cg_cln$paoc) |> 
  hux_corr() 
```

#### Level of Confidence x Burden Scale for Family Caregivers

```{r}
# Confidence x BSFC
cor.test(cg_cln$confidence, cg_cln$bsfc) |> 
hux_corr()
```

### Level of Support

```{r}
# Make Support a 3 Level Factor
support <- 
  cg_cln |> 
  mutate(
    support = case_when(
      support == "0" ~ "No Support",
      support == "1" ~ "Some Support",
      support == "2" ~ "Support"
    )
  ) |> 
  select(support,bsfc,paoc)
```

#### Support and PAOC

```{r}
# Level of Support and PAOC Score
aov(support$paoc~support$support) |> 
  # Use aov_car to clean up
  summary()
```

#### Support and BSFC

```{r}
# Level of Support and BSFC Score
aov(support$bsfc~support$support) |> 
  # Use aov_car to clean up
  summary()
```

#### Figures

```{r}
# Plot: Support and BSFC
support |> 
  ggplot(aes(support,bsfc)) + 
  stat_summary(
    fun.data = "mean_se",
    aes(color = support)
  ) +
  geom_quasirandom() +
  labs(
    x = "\nLevel of Support from Friends and Family\n",
    y = "Burden Scale for Family Caregivers Score\n",
    color = "Degree of Support"
  ) +
  scale_color_manual(
    values = wes_palette(15)
  )
```

```{r}
# Plot: Support and PAOC
support |> 
  ggplot(aes(support,paoc)) + 
  stat_summary(
    fun.data = "mean_se",
    aes(color = support)
  ) +
  geom_quasirandom() +
  labs(
    x = "\nLevel of Support from Friends and Family\n",
    y = "Positive Aspects of Caregiving Score\n",
    color = "Degree of Support"
  ) +
  scale_color_manual(
    values = wes_palette(15)
  )
```

### Priming Negative vs Positive

#### Priming and BSFC

```{r}
pr_bsfc <- 
  t.test(cg_cln$bsfc ~ cg_cln$condition, var.equal = T) |> 
  hux_tt()

pr_bsfc$grp1[1] <- "Negative"
pr_bsfc$grp2[1] <- "Positive"

pr_bsfc
```

#### Priming and PAOC

```{r}
pr_paoc <- 
  t.test(cg_cln$paoc ~ cg_cln$condition, var.equal = T) |> 
  hux_tt()

pr_paoc$grp1[1] <- "Negative"
pr_paoc$grp2[1] <- "Positive"

pr_paoc
```
